---
title: "Using AlphaSimHlpR to simulate a breeding program with AlphaSimR"
author: 
- Jean-Luc Jannink
date: "2020-01-05"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using AlphaSimHlpR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

AlphaSimR is a package with many useful functions to simulate plant and animal breeding schemes. But it is not very easy to implement. AlfSimHlpR defines functions that provide structure for a breeding scheme 

## Using AlfSimHlpR

```{r Load packages}
# Make sure you have the right packages installed
neededPackages <- c("AlphaSimR", "dplyr", "tidyr", "plotrix", "lme4", "sommer", "optiSel")
for (p in neededPackages) if (!require(p, character.only=T)) install.packages(p)
suppressMessages(library(AlphaSimHlpR))
```

### Define simulation settings
Define the genetic architecture of the population and other breeding scheme parameters in a list `bsp`.
```{r Define Population}
bsp <- specifyPopulation(ctrlFileName="../inst/PopulationCtrlFile_Small.txt")
bsp <- specifyPipeline(bsp, ctrlFileName="../inst/ControlFile_Small.txt")
bsp <- specifyCosts(bsp, ctrlFileName="../inst/CostsCtrlFile_Small.txt")
print(bsp)

nReplications <- 3
bsp$nCyclesToRun <- 6
```

### Run a simple breeding scheme for `r bsp$nCyclesToRun` cycles
Replicate a very simple breeding program `r nReplications` times. 
```{r Replicate Scheme}
replicRecords <- lapply(1:nReplications, runBreedingScheme, nCycles=bsp$nCyclesToRun, initializeFunc=initFuncADChk, productPipeline=prodPipeFncChk, populationImprovement=popImprov1Cyc, bsp)
```

### Calculate the means of the breeding programs
And plot them out
```{r Calculate means}
plotData <- plotRecords(replicRecords)
meanMeans <- tapply(plotData$genValMean, list(plotData$year, plotData$stage), mean)
meanMeans <- meanMeans[,c("F1", bsp$stageNames)]
stdErrMeans <- tapply(plotData$genValMean, list(plotData$year, plotData$stage), std.error)
stdErrMeans <- stdErrMeans[,c("F1", bsp$stageNames)]
print(meanMeans)
print(stdErrMeans)
```
